Scikit-learn: machine learning without learning the machinery

### 2014-05-19 article.tex
fixes for NLP section

In the NLP application domain,
features are typically 
where features are typically frequencies or boolean indicators
of very large numbers of rare events, such as
``document contains the term \textsf{v1agr@}'' (spam filtering)
or ``next token matches the Roman numeral regex'' (named-entity recognition).
To ensure scalability in the face of such data,
SciPy's sparse matrix data structures are supported by many estimators.\footnote{
  Support for these is added on a by-need basis,
  because using sparse data structures puts constraints on algorithm design
  and implementation.
}

@@

This script first fetches the hand-labeled movie review dataset from
\cite{pang2004} and unpacks it to disk using standard Python libraries.
It then loads these into memory using the scikit-learn function
\texttt{load\_files}, makes a pipeline of a \textsf{tf--idf} feature extractor
\cite{rennie2003tackling} and logistic regression,
and finally trains the model.
The parameters for the feature extractor and the LogReg classifier
were tuned offline; the random-number generator seed is set by hand
to get reproducible results.

Does this classifier work?
We can find out by classifying some of our own movie reviews.\footnote{
  The code can be tried interactively by simply copy-pasting it
  into an interactive Python interpreter or IPython \cite{perez2007ipython}.
}

>>>>

In the NLP application domain,
features are typically frequencies or boolean indicators
of very large numbers of rare events.
In document classification tasks such spam filtering,
these events may be booleans indicating
``document contains the term \textsf{v1agr@}''
(and so on for all words encountered in the training set).
In other NLP problems such as finding proper names and their classes (NER),
events such as ``next token matches the Roman numeral regex'' may be used.
To ensure scalability in the face of such extremely high-dimensional data,
SciPy's sparse matrix data structures are supported by many estimators.\footnote{
  Support for these is added on a by-need basis,
  because using sparse data structures puts constraints on algorithm design
  and implementation.
}

@@

This script first fetches the hand-labeled movie review dataset from
\cite{pang2004} and unpacks it to disk using standard Python libraries.
It then loads these into memory using the scikit-learn function
\texttt{load\_files}, makes a pipeline of a \textsf{tf--idf} feature extractor
\cite{rennie2003tackling} and logistic regression,
and finally trains the model.
The feature extractor (vectorizer) takes text as strings
and produces a sparse matrix of weights based on frequencies.
The parameters for the feature extractor and the LogReg classifier
were tuned offline; the random-number generator seed is set by hand
to get reproducible results.

Does this classifier work?
We can find out by classifying two of our own movie reviews.\footnote{
  The code can be tried interactively by simply copy-pasting it
  into an interactive Python interpreter or IPython \cite{perez2007ipython}.
}
